Supplement to Manuscript for MADA Project

### 2023-04-08 code/analysis_code/statistical_analysis/1_model_fitting/model_fitting.Rmd
Part 4 Additional Updates

# Looking at the summary of log_fit_fullmodel
table2 <- tidy(log_fit_fullmodel)
table2
saveRDS(table2, file = (here("results", "statistical_analysis_result", "model_fitting_result", "full_model.rds")))
```

@@

# Looking at the summary of log_fit_year_age_hispanic
table3 <- tidy(log_fit_year_age_hispanic)
saveRDS(table3, file = (here("results", "statistical_analysis_result", "model_fitting_result", "year_age_hispanic_model.rds")))
```

@@

# Looking at the summary of log_fit_demographic
table4 <- tidy(log_fit_demographic)
saveRDS(table4, file = (here("results", "statistical_analysis_result", "model_fitting_result", "demographic_model.rds")))
```

@@

# Looking at the summary of log_fit_medical
table5 <- tidy(log_fit_medical)
saveRDS(table5, file = (here("results", "statistical_analysis_result", "model_fitting_result", "medical_model.rds")))
```

@@

# Looking at the summary of log_fit_smoking_alcohol
table6 <- tidy(log_fit_smoking_alcohol)
saveRDS(table6, file = (here("results", "statistical_analysis_result", "model_fitting_result", "smoking_alcohol_model.rds")))
```

@@

# Saving model_performance result
saveRDS(table7, file = (here("results", "statistical_analysis_result", "model_fitting_result", "model_performance_comparison.rds")))
```

>>>>

# Looking at the summary of log_fit_fullmodel
table2 <- tidy(log_fit_fullmodel)
table2
saveRDS(table2, file = (here("results", "statistical_analysis_result", "1_model_fitting_result", "full_model.rds")))
```

@@

# Looking at the summary of log_fit_year_age_hispanic
table3 <- tidy(log_fit_year_age_hispanic)
saveRDS(table3, file = (here("results", "statistical_analysis_result", "1_model_fitting_result", "year_age_hispanic_model.rds")))
```

@@

# Looking at the summary of log_fit_demographic
table4 <- tidy(log_fit_demographic)
saveRDS(table4, file = (here("results", "statistical_analysis_result", "1_model_fitting_result", "demographic_model.rds")))
```

@@

# Looking at the summary of log_fit_medical
table5 <- tidy(log_fit_medical)
saveRDS(table5, file = (here("results", "statistical_analysis_result", "1_model_fitting_result", "medical_model.rds")))
```

@@

# Looking at the summary of log_fit_smoking_alcohol
table6 <- tidy(log_fit_smoking_alcohol)
saveRDS(table6, file = (here("results", "statistical_analysis_result", "1_model_fitting_result", "smoking_alcohol_model.rds")))
```

@@

# Saving model_performance result
saveRDS(table7, file = (here("results", "statistical_analysis_result", "1_model_fitting_result", "model_performance_comparison.rds")))
```

### 2023-04-08 code/analysis_code/statistical_analysis/2_model_evaluation/model_evaluation.Rmd
Part 4 Additional Updates

# Pulling the fitted model object and using tidy() function for getting a tidy tibble of model coefficients
data_clean_main_fit %>% 
  extract_fit_parsnip() %>% 
  tidy()
```

@@

# Pulling the fitted model object and using tidy() function for getting a tidy tibble of model coefficients
data_clean_main_fit2 %>% 
  extract_fit_parsnip() %>% 
  tidy()
```

>>>>

# Pulling the fitted model object and using tidy() function for getting a tidy tibble of model coefficients
data_clean_main_fit %>% 
  extract_fit_parsnip() %>% 
  tidy()

# Saving the above coefficients table
table8 <- data_clean_main_fit
saveRDS(table8, file = (here("results", "statistical_analysis_result", "2_model_evaluation_result", "logistic_full_model.rds")))
```

@@

# Pulling the fitted model object and using tidy() function for getting a tidy tibble of model coefficients
data_clean_main_fit2 %>% 
  extract_fit_parsnip() %>% 
  tidy()

# Saving the above coefficients table
table9 <- data_clean_main_fit2
saveRDS(table9, file = (here("results", "statistical_analysis_result", "2_model_evaluation_result", "logistic_outcome_mainpredictor.rds")))
```

### 2023-04-08 products/manuscript/Manuscript.qmd
Part 4 Additional Updates

# Loading the `full_model.rds` table which was created during the statistical analysis process
result_table2 <- readRDS(here("results", "statistical_analysis_result", "full_model.rds"))
print(result_table2, n = Inf, width = Inf)
```

>>>>

# Loading the `full_model.rds` table which was created during the statistical analysis process
result_table2 <- readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "full_model.rds"))
print(result_table2, n = Inf, width = Inf)
```

### 2023-04-08 products/supplement/Supplementary_Material.qmd
Part 4 Additional Updates

```{r}
#| label: Additional Table 3
#| tbl-cap: "Fit table using mammogram status as the outcome and the medical characteristics as the predictors."
#| echo: FALSE
additionaltable1 = readRDS(here("results", "statistical_analysis_result", "medical_model.rds"))
knitr::kable(additionaltable3)
```

```{r}
#| label: Additional Table 4
#| tbl-cap: "Fit table using mammogram status as the outcome and smoking & alcohol characteristics as the predictors."
#| echo: FALSE
additionaltable1 = readRDS(here("results", "statistical_analysis_result", "smoking_alcohol_model.rds"))
knitr::kable(additionaltable4)
```

>>>>

```{r}
#| label: Additional Table 3
#| tbl-cap: "Fit table using mammogram status as the outcome and the medical characteristics as the predictors."
#| echo: FALSE
additionaltable3 = readRDS(here("results", "statistical_analysis_result", "medical_model.rds"))
knitr::kable(additionaltable3)
```

```{r}
#| label: Additional Table 4
#| tbl-cap: "Fit table using mammogram status as the outcome and smoking & alcohol characteristics as the predictors."
#| echo: FALSE
additionaltable4 = readRDS(here("results", "statistical_analysis_result", "smoking_alcohol_model.rds"))
knitr::kable(additionaltable4)
```

```{r}
#| label: Additional Table 5
#| tbl-cap: "Model fitting table using mammogram status as the outcome and demographic characteristics as the predictors."
#| echo: FALSE
additionaltable5 = readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "demographic_model.rds"))
knitr::kable(additionaltable5)
```

```{r}
#| label: Additional Table 6
#| tbl-cap: "Model fitting table using mammogram status as the outcome and medical characteristics as the predictors."
#| echo: FALSE
additionaltable6 = readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "medical_model.rds"))
knitr::kable(additionaltable6)
```

```{r}
#| label: Additional Table 7
#| tbl-cap: "Model fitting table using mammogram status as the outcome and smoking and alcohol characteristics as the predictors."
#| echo: FALSE
additionaltable7 = readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "smoking_alcohol_model.rds"))
knitr::kable(additionaltable7)
```

```{r}
#| label: Additional Table 8
#| tbl-cap: "Model fitting table using mammogram status as the outcome and year, age, and hispanic characteristics as the predictors."
#| echo: FALSE
additionaltable8 = readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "year_age_hispanic_model.rds"))
knitr::kable(additionaltable8)
```

```{r}
#| label: Additional Table 9
#| tbl-cap: "Model performance comparison."
#| echo: FALSE
additionaltable9 = readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "model_performance_comparison.rds"))
knitr::kable(additionaltable9)
```

```{r}
#| label: Additional Table 10
#| tbl-cap: "Model coefficients table using mammogram status as the outcome and other variables of interests as the predictors using model evaluation."
#| echo: FALSE
additionaltable10 = readRDS(here("results", "statistical_analysis_result", "2_model_evaluation_result", "logistic_full_model.rds"))
knitr::kable(additionaltable10)
```

```{r}
#| label: Additional Table 11
#| tbl-cap: "Model coefficients table using mammogram status as the outcome and hispanic status as the main predictor using model evaluation."
#| echo: FALSE
additionaltable11 = readRDS(here("results", "statistical_analysis_result", "3_machine_learning_result", "lasso_model_final_fit.rds"))
knitr::kable(additionaltable11)
```

```{r}
#| label: Additional Table 12
#| tbl-cap: "Lasso model final fit using machine learning approach."
#| echo: FALSE
additionaltable12 = readRDS(here("results", "statistical_analysis_result", "2_model_evaluation_result", "logistic_outcome_mainpredictor.rds"))
knitr::kable(additionaltable12)
```

```{r}
#| label: Additional Figure 1
#| fig-cap: "Decision tree model."
#| echo: FALSE
knitr::include_graphics("/results/statistical_analysis_result/3_machine_learning_result/figure2_decision_tree_model.png")
```

```{r}
#| label: Additional Figure 2
#| fig-cap: "Lasso model."
#| echo: FALSE
knitr::include_graphics("/results/statistical_analysis_result/3_machine_learning_result/figure3_lasso_model.png")
```
